Centralizers of higher enveloping algebras of Lie algebras

### 2020-08-27 draft.tex
bulk

\begin{thm}
\label{thm: centralizer}
Let $\UU_n \fg$ be the enveloping $E_n$ algebra of a dg Lie algebra $\fg$ and let $f: \UU_n \fg \to B$ a map of augmented $E_n$ algebras.
Then
\begin{itemize}
\item $f$ equips $B$ with the structure of an $E_n$ algebra in $\fg$-modules and
\item the centralizer ${\frak Z}_{E_n}(f)$ is an $E_n$-algebra modeled by the Chevalley-Eilenberg 
cochains $\clies(\fg, B)$ equipped with the convolution $E_n$-product.
\end{itemize}
\end{thm}

@@

Now, for any $E_n$-algebra the factorization homology along the $(n-1)$-sphere $\int_{S^{n-1}} A$ is an $E_1$-algebra.
By Proposition 3.33 of \cite{FrancisHH} (see also Example 5.5.4.16 of \cite{LurieHA}), there is an equivalence of $\infty$-categories ${\rm Mod}^{E_n}_A (\Ch_k^{\otimes_k}) \simeq {\rm LMod}_{\int_{S^{n-1}} A} (\Ch_k^{\otimes_k})$.
For $A = \UU_n \fg$, the factorization homology along the $(n-1)$-sphere is $\int_{S^{n-1} A} \simeq \UU_1 \left(\fg[\epsilon] \right)$, where $\epsilon$ is a formal parameter of cohomological degree $n-1$.
It follows that there is an equivalence of $\infty$-categories 
\[
{\rm Mod}_{\UU_n \fg}^{E_n} (\Ch_k^{\otimes_k}) \simeq {\rm LMod}_{\UU_1(\fg[\epsilon])} (\Ch_k^{\otimes_k}) = {\rm Mod}_{\fg[\epsilon]} (\Ch_k^{\otimes_k}) .
\]
\brian{The RHS has a symmetric monoidal structure with $\otimes_k$. 
This does not agree with the tensor product on the LHS, but we hope there is a functor $\otimes_{\UU_n \fg} \to \otimes_k$.}

@@

First note that compactly supported form embedds in all forms, therefore we can apply 
any element of $\cliels\big(\fg \otimes \Omega^* (-), B(-)\big)$ 
to any element of $\cliels\big(\fg \otimes \Omega_c^* (-)\big)$. Therefore, for any  $p\in \bN$, we have an evaluation 
\begin{equation} \label{eqdef:ev} \begin{array}{c}\ev: Sym^p \big( \fg \otimes \Omega^* (U)[-1] ,B(U)\big)
\otimes  Sym^p( \fg\otimes \Omega^*_c(U) [1]) \stackrel{ev}\longrightarrow B(U)  
  \\
 (x,\Phi) \,\longmapsto\, (-1)^{p(|x|+p) } \Phi (x)\end{array}
\end{equation} induced by this embedding  in all forms followed by evaluating on a function.

@@

\brian{do you like this example?} \greg{I do !}
\begin{eg}\label{eg: TT}
Consider the case $n=1$ and $B = U \fg$ where $f$ is simply the identity map. 
A classic result of \cite{HochSerre} is that the Hochschild cohomology of $U \fg$ can be expressed in terms of Lie algebra cohomology as $\Hoch^*(U\fg,U\fg) \simeq \clies(\fg, U\fg^{ad})$. 
On the right-hand side, we take the Chevalley--Eilenberg cochain complex with values in the module $U \fg$ equipped with the adjoint action.
The algebra structure is given by a special case of the convolution product as in Section \ref{??}.

@@

Our model also gives us a simple description of the factorization homology of the derived center along the circle $S^1$.
\[
\int_{S^1} {\frak Z}(U(\fg)) \simeq \clies(\fg[\epsilon], \cliels( \fg[\epsilon])),
\]
where $\epsilon$ is a formal variable of degree~$1$. 
\brian{We should compare with Tamarkin-Tsygan's noncommutative calculus (cf. section 2.6).
We could exhibit Theorem 2.7.1 explicitly in this case for the $E_n$ case with enveloping algebras.}
\end{eg}

>>>>

\begin{thm}
\label{thm: centralizer}
Let $\UU_n \fg$ be the enveloping $E_n$ algebra of a dg Lie algebra $\fg$ and let 
\[
f: \UU_n \fg \to B
\]
be a map of augmented $E_n$ algebras.
Then
\begin{itemize}
\item $f$ equips $B$ with the structure of an $E_n$ algebra in $\fg$-modules and
\item the centralizer ${\frak Z}_{E_n}(f)$ is an $E_n$-algebra modeled by the Chevalley-Eilenberg 
cochains $\clies(\fg, B)$ equipped with the convolution $E_n$-product.
\end{itemize}
\end{thm}

@@

Now, for any $E_n$-algebra the factorization homology along the $(n-1)$-sphere $\int_{S^{n-1}} A$ is an $E_1$-algebra.
By Proposition 3.33 of \cite{FrancisHH} (see also Example 5.5.4.16 of \cite{LurieHA}), there is an equivalence of $\infty$-categories ${\rm Mod}^{E_n}_A (\Ch_k^{\otimes_k}) \simeq {\rm LMod}_{\int_{S^{n-1}} A} (\Ch_k^{\otimes_k})$.
For $A = \UU_n \fg$, the factorization homology along the $(n-1)$-sphere is $\int_{S^{n-1}} A \simeq \UU_1 \left(\fg[\epsilon] \right)$, where $\epsilon$ is a formal parameter of cohomological degree $n-1$.
It follows that there is an equivalence of $\infty$-categories 
\[
{\rm Mod}_{\UU_n \fg}^{E_n} (\Ch_k^{\otimes_k}) \simeq {\rm LMod}_{\UU_1(\fg[\epsilon])} (\Ch_k^{\otimes_k}) = {\rm Mod}_{\fg[\epsilon]} (\Ch_k^{\otimes_k}) .
\]
\brian{The RHS has a symmetric monoidal structure with $\otimes_k$. 
This does not agree with the tensor product on the LHS, but we hope there is a functor $\otimes_{\UU_n \fg} \to \otimes_k$.}

@@

First note that compactly supported form embeds in all forms, therefore we can apply 
any element of $\cliels\big(\fg \otimes \Omega^* (-), B(-)\big)$ 
to any element of $\cliels\big(\fg \otimes \Omega_c^* (-)\big)$. Therefore, for any  $p\in \bN$, we have an evaluation 
\begin{equation} \label{eqdef:ev} \begin{array}{c}\ev: Sym^p \big( \fg \otimes \Omega^* (U)[-1] ,B(U)\big)
\otimes  Sym^p( \fg\otimes \Omega^*_c(U) [1]) \stackrel{ev}\longrightarrow B(U)  
  \\
 (x,\Phi) \,\longmapsto\, (-1)^{p(|x|+p) } \Phi (x)\end{array}
\end{equation} induced by this embedding  in all forms followed by evaluating on a function.

@@

\subsection{Koszul duality}
\label{sec: Koszul}

Consider the trivial $E_n$-algebra $k$ and suppose $\varepsilon : \UU_n \fg \to k$ is the natural augmentation. 
Then, ${\frak Z}_n (\varepsilon)$ is the $E_n$-{\em Koszul dual} of the $E_n$-algebra $\UU_n \fg$. 
Our results provide a model for this $E_n$-algebra as a locally constant factorization algebra on $\RR^n$ which assigns to an open set $U \subset \RR^n$ the cochain complex
\[
\clie \left(\fg \otimes \Omega(U) \right) .
\]

\subsection{Universal bulk TFT}
\label{sec: TFT}

Generally speaking, the local observables of a topological field theory on a manifold $M$ form a locally constant factorization algebra on $M$.

Let $\fg$ be a dg Lie algebra and consider the $E_n$ algebra $\UU_n \fg$. 
We have shown that a model for the $E_n$-center ${\frak Z}_n (\UU_n \fg) = {\frak Z}_n ({\rm id}_{\UU_n \fg})$ is the $n$-dimensional locally constant factorization algebra 
\[
\clie \left( \fg \otimes \Omega \; , \; \clieu (\fg \otimes \Omega_c) \right)  .
\]

Let us place this locally constant factorization algebra on the $n$-manifold $M$.
This factorization algebra is equivalent to the pushforward of a factorization algebra $\cF_{\rm bulk}$ on the $(n+1)$-dimensional manifold $M \times \RR$ along the projection $\pi : M \times \RR \to M$. 
We proceed to construct this factorization algebra.

For an open set $V \subset M \times I$ let $\cF^{\rm cl}_{\rm bulk} (V)$ be the cochain complex 
\[
\cF^{\rm cl}_{\rm bulk} (V) = \clie \bigg(\fg \otimes \Omega (V) \; , \; \Sym \left(\fg \otimes \Omega_c(V) [2] \right) \bigg) .
\]
The assignment $V \mapsto \cF^{\rm cl}_{\rm bulk}(V)$ defines a locally constant factorization algebra $\cF^{\rm cl}_{\rm bulk}$ on $M \times \RR$.

The factorization algebra $\pi_* \cF^{\rm cl}_{\rm bulk}$ on $M$ is quasi-isomorphic to a certain limit, or ``deqauntization", of the $E_n$-center of $\UU_n \fg$. 
To exhibit this quasi-isomorphism, we introduce the following cochain maps.
For an open set $U \subset M$ let
\[
\int_\RR : \Omega_c(U \times \RR) \to \Omega_c (U) [1] 
\] 
be the map which integrates a compactly supported form on $U \times \RR$ along $\RR$. 
This map is a quasi-isomorphism for any $U $ and admits the following explicit retract. 
Let $\phi$ be a fixed compactly supported function on $\RR$ of mass $1$ and define
\[
r_\phi : \Omega_c(U) [1] \to \Omega_c (U \times \RR)
\]
by $r_\phi (\alpha) = \alpha \wedge \phi \, \d t$.

The ``dequantization" of the $E_n$-center is defined using the following filtration of ${\frak Z}_n(\UU_n \fg)$.
We for any Lie algebra $\fh$, let $\clieu_{\leq k} (\fh)$ be the subcomplex of Chevalley--Eilenberg chains which is $\Sym^{\leq k} (\fh[1])$ as an underlying graded vector space. 
The increasing filtration for the $E_n$-center is defined by
\[
F^k {\frak Z}_n(\UU_n \fg) = \clie \bigg(\fg \otimes \Omega \; , \; \clieu_{\leq k} (\fg \otimes \Omega_c) \bigg) .
\]
This is a filtration of factorization algebras on $M$. 
The associated graded factorization algebra is
\[
{\rm Gr} \;  {\frak Z}_n(\UU_n \fg)  = \clie \bigg(\fg \otimes \Omega \; , \; \Sym \left(\fg \otimes \Omega_c [1] \right) \bigg) .
\]
Notice this is similar to the model $E_n$-center except we have turned off the Chevalley--Eilenberg differential on chains.

\begin{lmm}
Integration along $\RR$ determines a quasi-isomorphism of factorization algebras on $M$:
\[
\int_\RR : \pi_* \cF^{\rm cl}_{\rm bulk} \xto{\simeq} {\rm Gr} \;  {\frak Z}_n(\UU_n \fg) .
\]
In fact, this is a deformation retraction with retract given by $r_\phi$. 
\end{lmm}

\brian{Maybe you can finesse this last part better than me.}

%\begin{lmm}
%Consider the locally constant factorization algebra $\cF_{\rm bulk}$ on $M \times \RR$ which assigns to an open set $U \subset M \times \RR$
%\[
%\cF_{\rm bulk} = \clie \left(\fg \otimes \Omega (U) \; , \; \clieu (\fg \otimes \Omega_c (U)[1]) \right) .
%\]
%Then, 
%\end{lmm}
%
%\begin{proof}
%For $V \subset M$, the integration of compactly supported de Rham forms along $\RR$ 
%\[
%\fg \otimes \Omega_c (\pi^{-1} (V)) = \fg \otimes \Omega_c (V \times \RR) \xto{\int_{\RR}} \fg \otimes \Omega_c (V) [-1] .
%\]
%is a quasi-isomorphism. 
%
%\end{proof}

\subsection{$E_n$-calculus}
\label{sec: TT}

\brian{HKR}

Consider the case $n=1$ and $B = U \fg$ where $f$ is simply the identity map. 
A classic result of \cite{HochSerre} is that the Hochschild cohomology of $U \fg$ can be expressed in terms of Lie algebra cohomology as $\Hoch^*(U\fg,U\fg) \simeq \clies(\fg, U\fg^{ad})$. 
On the right-hand side, we take the Chevalley--Eilenberg cochain complex with values in the module $U \fg$ equipped with the adjoint action.
The algebra structure is given by a special case of the convolution product as in Section \ref{??}.

@@

Our model also gives us a simple description of the factorization homology of the derived center along the circle $S^1$.
\[
\int_{S^1} {\frak Z}(U(\fg)) \simeq \clies(\fg[\epsilon], \cliels( \fg[\epsilon])),
\]
where $\epsilon$ is a formal variable of degree~$1$. 
\brian{We should compare with Tamarkin-Tsygan's noncommutative calculus (cf. section 2.6).
We could exhibit Theorem 2.7.1 explicitly in this case for the $E_n$ case with enveloping algebras.}
